Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2005-09-03 paper/introduction.tex
Make the bibliography correct

Since their introduction~\cite{weiner}, suffix trees have been one of the methods of choice for text indexing. Suffix trees solve the following problem: given a text which has been preprocessed, and a pattern, efficiently find the places in the text where this pattern occurs.  However, for many real-life problems this is too restrictive. In this class of problems, one is interested in finding places in the text where an approximate form of the pattern occurs. Several algorithms have been proposed to solve this problem. \cite{navarro:guided} presents a survey of the problem and existing approaches to solving it at the time that work was written. Recently there have been some further work in the field, notably~\cite{maass:text} which also contains an updated overview of methods for solving the problem in addition to presenting one itself.

@@

Our work is related to efforts to index the text for approximate matching such as~\cite{maass:text,mosche}. The structure presented is superficially very similar to the one presented in~\cite{inexact} as an \textit{inexact suffix tree} though that work is concerned with solving a different set of problems.

>>>>

Since their introduction~\cite{DBLP:conf/focs/Weiner73}, suffix trees have been one of the methods of choice for text indexing. Suffix trees solve the following problem: given a text which has been preprocessed, and a pattern, efficiently find the places in the text where this pattern occurs.  However, for many real-life problems this is too restrictive. In this class of problems, one is interested in finding places in the text where an approximate form of the pattern occurs. Several algorithms have been proposed to solve this problem. \cite{navarro:guided} presents a survey of the problem and existing approaches to solving it at the time that work was written. Recently there have been some further work in the field, notably~\cite{maass:text} which also contains an updated overview of methods for solving the problem in addition to presenting one itself.

@@

Our work is related to efforts to index the text for approximate matching such as~\cite{maass:text,amir00oneerror}. The structure presented is superficially very similar to the one presented in~\cite{DBLP:journals/tcs/ChattarajP05} as an \textit{inexact suffix tree} though that work is concerned with solving a different set of problems and the algorithms presented are fundamentally different.

### 2005-09-03 paper/structure.tex
Make the bibliography correct

Suffix Trees have become a well known structure since their introduction in 1973~\cite{weiner}. In Figure~\ref{fig:mississippi-0} we show the suffix tree for the string \putstring{mississippi}.

@@

The name Patricia is sometimes spelled PATRICIA, since it was formed from the initial of Practical Algorithm to Retrieve Information Coded in Alphanumeric~\cite{morrison:patricia}.

@@

In a suffix tree, it is possible to define a suffix link for each internal node. Both Ukkonen's~\cite{ukkonen} and McCreight's~\cite{mccreight} algorithms are linear time algorithms for constructing a suffix tree which includes suffix links. The suffix links are shown in Figure~\ref{fig:mississippi-0} as dotted links.

>>>>

Suffix Trees have become a well known structure since their introduction in 1973~\cite{DBLP:conf/focs/Weiner73}. In Figure~\ref{fig:mississippi-0} we show the suffix tree for the string \putstring{mississippi}.

@@

The name Patricia is sometimes spelled PATRICIA, since it was formed from the initial of Practical Algorithm to Retrieve Information Coded in Alphanumeric~\cite{DBLP:journals/jacm/Morrison68}.

@@

In a suffix tree, it is possible to define a suffix link for each internal node. Both Ukkonen's~\cite{ukkonen92constructing} and McCreight's~\cite{mccreight} algorithms are linear time algorithms for constructing a suffix tree which includes suffix links. The suffix links are shown in Figure~\ref{fig:mississippi-0} as dotted links.
